Implementing Distributed Systems Directly\\with I/O Automata in ioa++

### 2011-10-01 papers/paper1/component_model.tex
Fixes through page 6.

% A dynamic system implies that the system $S$ must be dependent on time $t$ as a function of the number of actions that have been executed by $t$.
% Thus, $S_{t+1}$ need not be equal to $S_{t}$.
% A \emph{system action} is an action that \emph{can} change the system $S$.
% The set of automata $A$ and set of bindings $B$ are managed by the \emph{system automaton} which represents the run-time system.
As Figure~\ref{system_action} illustrates, the system automaton provides: parameterized input actions for receiving requests to create, bind, unbind, and destroy automata; internal actions for evaluating and enacting system action requests; and corresponding parameterized output actions through which to return results of the requests.
The base automaton provides output actions that trigger requests to create, bind, unbind, and destroy automata, along with
input actions to receive the results.
User-defined component automata (i.e., \emph{user automata}) inherit from the base automaton, which as we describe in Section~\ref{framework_architecture} is implemented in ioa++ as a C++ class. 
Each user automaton is thus composed (not bound) with the system automaton and inherits output actions for requesting system actions and input actions for receiving the results of system actions.

@@

To allow a dynamic system to provide semantics consistent with a static system, the execution of output actions must be delayed until the set of implied automata matches the set implied by the static system.
To do this, we take the conjunction of the precondition of an output action with a predicate over the set of bindings $B$ (called a \emph{binding predicate}) to ensure that the output action is not executed until its set of implied automata is correct.
Notice that this only requires reading $B$ and is permitted since all updates to $B$ are serialized as was previously discussed.
Thus, a dynamic system can be analyzed as a static system by ignoring system actions and the binding predicates.
A system defined statically can be implemented as a dynamic system by adding binding predicates and logic to create the required constellation of automata.

>>>>

% A dynamic system implies that the system $S$ must be dependent on time $t$ as a function of the number of actions that have been executed by $t$.
% Thus, $S_{t+1}$ need not be equal to $S_{t}$.
% A \emph{system action} is an action that \emph{can} change the system $S$.
% The set of automata $A$ and set of bindings $B$ are managed by the \emph{system automaton} which represents the run-time system.
As Figure~\ref{system_action} illustrates, the system automaton provides: parameterized input actions for receiving requests to create, bind, unbind, and destroy automata; internal actions for evaluating and enacting system action requests; and corresponding parameterized output actions for returning responses to system action requests.
(Parameterized actions are indicated with [].)
The base automaton provides output actions that trigger requests to create, bind, unbind, and destroy automata, along with
input actions to receive the results.
User-defined component automata (i.e., \emph{user automata}) inherit from the base automaton, which as we describe in Section~\ref{framework_architecture} is implemented in ioa++ as a C++ class. 
Each user automaton is thus composed (not bound) with the system automaton and inherits output actions for requesting system actions and input actions for receiving the results of system actions.

@@

To allow a dynamic system to provide semantics consistent with a static system, the execution of output actions must be delayed until the set of implied automata matches the set implied by the static system.
To do this, we take the conjunction of the precondition of an output action with a predicate over the set of bindings $B$ (called a \emph{binding predicate}) to ensure that the output action is not executed until its set of implied automata is correct.
Thus, a dynamic system can be analyzed as a static system by ignoring system actions and the binding predicates.
A system defined statically can be implemented as a dynamic system by adding binding predicates and logic to create the required constellation of automata.
